An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-28 4_method.tex
Tim: rewrite 3.5

\paragraph{Beading} 
We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
For our distributed beading scheme we define the beading for a central node $v$ with $n = b^\wedge_v$ beads as:
\begin{align*}
    %B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
    B &= \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right)\\
    w_i &= 2R(v) / n  & \text{for all $i \leq n$}\\
    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i \leq n$}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

The beading information will be used in the next phase to directly generate the sites of the toolpaths.
Note that a beading conceptually covers the whole diameter, while we only apply it along the radii;
the upper half of the beading is therefore unused.

@@

>>>>

\paragraph{Beading} 
We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
For our distributed beading scheme we define the beading for a central node $v$ with $n = b^\wedge_v$ beads and a diameter $d = 2R(v)$  as:
\begin{align*}
    %B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
    B(n,d) &= \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right)\\
    w_i &= 2R(v) / n  & \text{for all $i \leq n$}\\
    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i \leq n$}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

\paragraph{Beading interpolation}
The beading is defined in terms of an integer number of beads, while we have assigned a fractional bead count to nodes within a transition region.
In order to generate a beading for a node $v$ with $n < b^*_v < n+1 $ we linearly interpolate the bead width and location of the first and last $n/2$ lines between a beading $B^V$ based on $n$ and a beading $B^W$ based on $n+1$ (see \cref{beading_interpolation}).
Such interpolation is also used to deal with beading conflicts (see \cref{beading_conflict_problem}).
We therefore also apply beading interpolation from a marked node $v_m$ upward along unmarked bones,
and interpolate between $v_m$ and the beading at the top of the slope over some distance $t_\text{beading}$ from the lower marked node.

\paragraph{Beading propagation}
The beading information is then broadcasted throughout the ST from central regions outward,
so that each unmarked node $v$ knows the beading of the marked node on top of the ramp on which $v$ is placed.
We first broadcast the beading information upward from all marked nodes,
so that we can then deal with beading conflicts in a downward phase.
This the downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.

\iffalse
The beading information will be used in the next phase to directly generate the sites of the toolpaths.
Note that a beading conceptually covers the whole diameter, while we only apply it along the radii;
the upper half of the beading is therefore unused.

@@

\fi
